OSF management

### 2021-03-24 RR_manuscript/Draft_RR.Rmd
:bento: - update osf data; edit RR

In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
In recent coordinated efforts to replicate published findings, scientific disciplines have uncovered surprisingly low success rates [e.g., @open2015estimating; @camerer2018evaluating] leading to what is now referred to as the *replication crisis*.
<!-- TODO: add REFS about variable conclusions from reliable data -->
Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data.
The latter situation has been referred to as the *inference crisis* [@rotello2015more; @starns2019assessing] and is, among other things, rooted in the inherent flexibility of data analysis [often referred to as researcher degrees of freedom: @simmons2011false; @gelman2014statistical].
Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
Along the way, different methodological and analytic choices need to be made, all of which may influence the final interpretation of the data.
These researcher degrees of freedom are both a blessing and a curse.

@@

When looking at phrase-level temporal domains, the number of possible analytic pipelines increases exponentially.
This plurality of analytic paths is illustrated in Figure \@ref(fig:forkingPaths).
Even if we have decided to compare fundamental frequency (f0) of only the word *another* across the two utterances, there are still many choices to be made, all of which need to be justified.
For example, we could measure f0 at specific points in time like the onset of the window, the offset, or the midpoint.
We could also measure the value or time of the minimum or maximum f0 value.
We could summarize f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyze speech data [see @gordon2017acoustic].
And the garden of forking paths does not stop here.
<!-- TODO: add examples of pitch tracking options -->
Figure \@ref(fig:forkingPaths), illustrates a specific option to automatically calculate f0.
Knowing that the signals and the measures thereof can be noisy, another option would be to smooth them using one algorithm and degree over others, or remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
<!-- NOTE: (JVC) Im having a bit of trouble with this sentence. I tried to fix it and now I am realizing I don't quite follow (JVC) -->

@@

<!-- TODO: ask people if they have ever heard of these papers -->

To further illuminate the question of whether speakers modify speech to signal atypical referents, thirty native German speakers were recorded while interacting with a confederate (one of the experimenters) in a referential game.
The participants had to verbally instruct the confederate to select a specified target object out of four object presented on a screen.
\Cref{f:procedural-timeline}
The subject and confederate were seated at the opposite sides of a table, each facing one of two mirrored computer screens.
The participant and the experimenter could not see each other nor each others' screens.
<!-- TODO: add ref to experiment procedure figure in (see XXX) -->
After a familiarization phase (see XXX), the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.
One of the objects served as the target, another as the competitor, and the remaining two objects served as distractors.
Objects were referred to using noun phrases consisting of an adjective modifier denoting color and a modified object (e.g. *Gelbe Zitrone* 'yellow lemon', *Rote Gurke* 'red cucumber', *Rote Socken* 'red socks').

>>>>

In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
In recent coordinated efforts to replicate published findings, scientific disciplines have uncovered surprisingly low success rates [e.g., @open2015estimating; @camerer2018evaluating] leading to what is now referred to as the *replication crisis*.
Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data.
The latter situation has been referred to as the *inference crisis* [@rotello2015more; @starns2019assessing] and is, among other things, rooted in the inherent flexibility of data analysis [often referred to as researcher degrees of freedom: @simmons2011false; @gelman2014statistical].
Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
Along the way, different methodological and analytic choices need to be made, all of which may influence the final interpretation of the data.
These researcher degrees of freedom are both a blessing and a curse.

@@

When looking at phrase-level temporal domains, the number of possible analytic pipelines increases exponentially.
This plurality of analytic paths is illustrated in Figure \@ref(fig:forkingPaths).
Even if we have decided to compare fundamental frequency (f0) of only the word *another* across the two utterances, there are still many choices to be made, all of which need to be justified.
For example, we could measure f0 at specific points in time like the onset of the window, the offset, or the midpoint.
We could also measure the value or time of the minimum or maximum f0 value.
We could summarize f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyze speech data [see @gordon2017acoustic].
And the garden of forking paths does not stop here.
Figure \@ref(fig:forkingPaths), illustrates a specific option to automatically calculate f0.
Knowing that the signals and the measures thereof can be noisy, another option would be to smooth them using one algorithm and degree over others, or remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
<!-- NOTE: (JVC) Im having a bit of trouble with this sentence. I tried to fix it and now I am realizing I don't quite follow (JVC) -->

@@

To further illuminate the question of whether speakers modify speech to signal atypical referents, thirty native German speakers were recorded while interacting with a confederate (one of the experimenters) in a referential game.
The participants had to verbally instruct the confederate to select a specified target object out of four object presented on a screen.
\Cref{f:procedural-timeline}
The subject and confederate were seated at the opposite sides of a table, each facing one of two mirrored computer screens.
The participant and the experimenter could not see each other nor each others' screens.
After a familiarization phase (see XXX), the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.
One of the objects served as the target, another as the competitor, and the remaining two objects served as distractors.
Objects were referred to using noun phrases consisting of an adjective modifier denoting color and a modified object (e.g. *Gelbe Zitrone* 'yellow lemon', *Rote Gurke* 'red cucumber', *Rote Socken* 'red socks').

### 2021-03-24 osf/data/README.Rmd
:bento: - update osf data; edit RR

- The `norming/` directory holds the files of the norming study.
- The `production/` directory contains two subdirectories:
  - `audio/`: with `.wav` and `.TextGrid` files from the production experiment.
  - `trial-lists/`: with `.csv` files with info on the trials from the production experiment.

See the `README.md` files of each individual directory for more information about the contents.

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Data component
data_comp <- osf_comps %>% filter(name == "Data")
```

```{r data_files, include=TRUE}
osf_ls_files(data_comp) %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

>>>>

- The `norming/` directory holds the files of the norming study.
  - `images/`: re-colored images for the norming study.
  - `ratings/`: rating results of the norming study.
- The `production/` directory contains two subdirectories:
  - `audio/`: with `.wav` and `.TextGrid` files from the production experiment.
  - `trial-lists/`: with `.csv` files with info on the trials from the production experiment.

See the `README.md` files in each directory for more information about the contents.

### 2021-03-24 osf/manage-osf.Rmd
:bento: - update osf data; edit RR

# Retrieve OSF repo and components

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Data")
```

# List data_comp files

```{r data_files}
osf_ls_files(data_comp)
```

# Readme files

@@

```{r knit-readmes, message=FALSE, warning=FALSE}
files <- list.files("./osf/data", pattern = "[.]Rmd$", recursive = T, full.names = T)

for (f in files) {
  xfun::Rscript_call(rmarkdown::render, list(f))
}
```

```{r upload-readmes}
# A loop would be better

# data/ ----
osf_upload(data_comp, path = "./osf/data/README.md", conflicts = "overwrite", verbose = T)

data_comp_files <- osf_ls_files(data_comp)

# data/norming/ ----
raw <- data_comp_files %>% filter(name == "norming")

#### delete old readme ("overwrite" option fails)
old_readme <- osf_ls_files(data_comp, "norming", pattern = "README.md")
osf_rm(old_readme, check = FALSE)

#### upload new readme
osf_upload(
  raw,
  path = "./osf/data/norming/README.md",
  conflicts = "overwrite", verbose = T)

# data/norming/images/ ----
#### delete old readme
old_readme <- osf_ls_files(data_comp, "norming/images/", pattern = "README.md")
osf_rm(old_readme, check = FALSE)

#### upload new readme
audio <- osf_ls_files(data_comp, "norming", pattern = "images")
osf_upload(
  audio,
  path = "./osf/data/norming/images/README.md",
  conflicts = "overwrite", verbose = T)

# data/production/audio/ ----
#### delete old readme
# old_readme <- osf_ls_files(data_comp, "production/audio", pattern = "README.md")
# osf_rm(old_readme, check = FALSE)
# 
# #### upload new readme
# audio <- osf_ls_files(data_comp, "production", pattern = "audio")
# osf_upload(
#   audio,
#   path = "./osf/data/production/audio/README.md",
#   conflicts = "overwrite", verbose = T)

# data/production/trial-lists ----
#### delete old readme
# old_readme <- osf_ls_files(data_comp, "production/trial-lists", pattern = "README.md")
# osf_rm(old_readme, check = FALSE)
# 
# #### upload new readme
# trials <- osf_ls_files(data_comp, "production", pattern = "trial-lists")
# osf_upload(
#   trials,
#   path = "./osf/data/production/trial-lists/README.md",
#   conflicts = "overwrite", verbose = T)
```

# PDF of norming and production methods

```{r pdf-methods}
file.copy("./docs/methods_norm_prod/methods_norm_prod.pdf", "./osf/data/", overwrite = T)

osf_upload(data_comp, path = "./osf/data/methods_norm_prod.pdf", conflicts = "overwrite", verbose = T)
```

# Norming study

@@

```{r ratings-upload}
rats <- osf_ls_files(data_comp, "norming", pattern = "ratings")

# delete old tgs
osf_rm(rats, check = FALSE)
osf_mkdir(data_comp, "norming/ratings")

# upload new tgs
new_ratings <- list.files("./osf/data/norming/ratings", ".csv", full.names = TRUE)

rats <- osf_ls_files(data_comp, "norming", pattern = "ratings")
osf_upload(rats, new_ratings, conflicts = "overwrite", verbose = T, progress = T)
```

# Production study

## TextGrids

@@

```{r textgrids-upload}
audio <- osf_ls_files(data_comp, "production", pattern = "audio")

# delete old tgs
osf_rm(audio, check = FALSE)
osf_mkdir(data_comp, "production/audio")

# upload new tgs
new_tgs <- list.files("./osf/data/production/audio", ".TextGrid", full.names = TRUE)

audio <- osf_ls_files(data_comp, "production", pattern = "audio")
osf_upload(audio, new_tgs, conflicts = "overwrite", verbose = T, progress = T)
```

## Trial lists

@@

```{r tlists-upload}
trials <- osf_ls_files(data_comp, "production", pattern = "trial-lists")

# delete old trials
old_trials <- osf_ls_files(trials, pattern = ".csv", n_max = Inf)

for (file in 1:nrow(old_trials)) {
  osf_rm(old_trials[file,], check = FALSE)
}

# upload new trials
new_trials <- list.files("./osf/data/production/trial-lists/", ".csv", full.names = TRUE)

for (trial in new_trials) {
  osf_upload(
    trials,
    path = trial,
    conflicts = "overwrite", verbose = T
  )
}
```

>>>>

# Retrieve OSF Data component

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_data <- osf_retrieve_node("5agn9")
```

# Prepare files

## Readme files

@@

```{r knit-readmes, message=FALSE, warning=FALSE}
readme_rmds <- list.files("./osf/data", pattern = "[.]Rmd$", recursive = T, full.names = T)

for (f in readme_rmds) {
  xfun::Rscript_call(rmarkdown::render, list(f))
}
```

## Norming study

@@

## Production study

@@

@@

# Upload files

```{r upload-files, eval=FALSE}
osf_upload(osf_data, path = "./osf/data/norming", recurse = T, verbose = T)
osf_upload(osf_data, path = "./osf/data/production", recurse = T, verbose = T)
osf_upload(osf_data, path = "./osf/data/README.md", recurse = T, verbose = T)
osf_upload(osf_data, path = "./osf/data/methods_norm_prod.pdf", recurse = T, verbose = T)
```
